---
title: "PT2050 ENGO"
author: "Patrick Bixler"
date: "01/08/2021"
output: html_document
---

```{r message=FALSE, warning=FALSE, include=FALSE}


knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

```

```{r Clean Network Data, include=FALSE}
library(readr)
setwd("C:/Users/tenis/Desktop/Data_Projects/pt2050/")
source("rmarkdown_scripts/utils1.R")

#edgelist 
el1<-el1
e1<-as.matrix(el1)
e1[,1]=as.character(e1[,1])
e1[,2]=as.character(e1[,2])
e1[,3]=as.character(e1[,3])
e1[,4]=as.character(e1[,4])
e1[,5]=as.character(e1[,5])

#edgelist 
el2<-el2
e2<-as.matrix(el2)
e2[,1]=as.character(e2[,1])
e2[,2]=as.character(e2[,2])


g1<-graph_from_data_frame(d=el1,directed=TRUE) 
#Some stats like communities and clusters need undirected graphs. Mode = collapse creates an undirected link between any pair of connected nodes. Weight should be "the nature of the tie"==communicate (1); coordinate (2), collaborate (3) but have not coded this yet. 






g2<-graph_from_data_frame(d=el2,directed=TRUE) 
#Some stats like communities and clusters need undirected graphs. Mode = collapse creates an undirected link between any pair of connected nodes. Weight should be "the nature of the tie"==communicate (1); coordinate (2), collaborate (3) but have not coded this yet. 
#g1_un<-as.undirected(g1, mode= "collapse",edge.attr.comb=list(weight="sum", "ignore"))


#Create a nodelist for excel use 
gvis<-toVisNetworkData(g1)
nodelist<-gvis$nodes
nodelist<-nodelist[,1]
nodelist<-as.data.frame(nodelist)
names(nodelist)<-c("name")

write.csv(nodelist,file = "data/Nodelist.csv")

#Create a nodelist for excel use 
gvis2<-toVisNetworkData(g2)
nodelist2<-gvis2$nodes
nodelist2<-nodelist[,1]
nodelist2<-as.data.frame(nodelist2)
names(nodelist2)<-c("name")

write.csv(nodelist2,file = "data/Nodelist2.csv")
```
#ego-centric network measures
```{r echo=FALSE}
#Degree in 
setwd("C:/Users/tenis/Desktop/Data_Projects/pt2050/")

inDegree1<-igraph::degree(g1,mode="in")
outDegree1<-igraph::degree(g1,mode="out")
TotalDegree1<-as.data.frame(igraph::degree(g1))
betweenness1<-igraph::betweenness(g1, v = V(g1), directed = TRUE, weights = NULL,
  nobigint = TRUE, normalized = TRUE)
inCloseness1<-igraph::closeness(g1, vids = V(g1), mode = c("in"),normalized = TRUE)
outCloseness1<-igraph::closeness(g1, vids = V(g1), mode = c("out"),normalized = TRUE)
#eigen<-evcent(m1,g=1,gmode = "digraph",rescale=TRUE, ignore.eval=TRUE)
#removed eigen from this DF_Centrality
DF_Centrality1<-as.data.frame(cbind(rownames(TotalDegree1),inDegree1,outDegree1,TotalDegree1,betweenness1,inCloseness1,outCloseness1))
rownames(DF_Centrality1)<-NULL
DF_Centrality1<-as.data.frame(DF_Centrality1)
colnames(DF_Centrality1)[1]<-"name"
colnames(DF_Centrality1)[4]<-"TotalDegree"

par(mfcol = c(4,3)) 
hist(inDegree1)
hist(outDegree1)
hist(TotalDegree1)
hist(betweenness1)
hist(inCloseness1)
hist(outCloseness1)

dd.g1<-degree.distribution(g1)
d<-1:max(TotalDegree1)-1
ind<-(dd.g1 != 0)
plot(d[ind],dd.g1[ind],log="xy",col="blue",xlab=c("Log-degree"),ylab=c("Log-Intensity"),
     main="Log-Log Degree Distribution")

txengocentrality<-merge(DF_Centrality1, nodelist, by = "name")
write.csv(txengocentrality,file = "data/TX ENGO Centrality.csv")

loc <- read_csv("data/coordinates.csv",
                col_types = cols(X1 = col_skip()))

attr_nodelist<-merge(txengocentrality, loc, by = "name",all.x = TRUE)
input_attributes<-attr_nodelist
input_attributes$Orgtype[is.na(input_attributes$Orgtype)] <- "Federal Agency"
write.csv(attr_nodelist,file = "data/Nodelist.csv")
```
#Meeting network
```{r echo=FALSE}
el_meetings<-el1[which(el1$Type1_meeting=="1"),]
e_meetings<-as.matrix(el_meetings)

g1_meetings<-graph_from_data_frame(d=e_meetings,directed=TRUE) 

#plot(g1_meetings)

```
#Equity network
```{r echo=FALSE}
el_equity<-el1[which(el1$Type3_equity=="1"),]
e_equity<-as.matrix(el_equity)
g1_equity<-graph_from_data_frame(d=e_equity,directed=TRUE) 

#Define Attributes
for (i in 1:vcount(g1_equity))
{
V(g1_equity)[i]$county<-input_attributes$County[which(input_attributes$name==V(g1_equity)[i]$name)]
V(g1_equity)[i]$type<-input_attributes$Orgtype[which(input_attributes$name==V(g1_equity)[i]$name)]
V(g1_equity)[i]$address<-input_attributes$address[which(input_attributes$name==V(g1_equity)[i]$name)]
V(g1_equity)[i]$size<-input_attributes$TotalDegree[which(input_attributes$name==V(g1_equity)[i]$name)]
}

lnodes <- data.frame(label = c("Non-Governmental","Municipal/County", "State Agency","Federal Agency","University","Private","Austin","Dallas", "Houston", "San Antonio", "Others"),
color.background = c("white", "white", "white", "white", "white","white","green", "blue","red", "yellow", "#87CEEB"),
color.border = c("black","black","black","black","black","black","black","black","black","black","black"),
shape=c("dot","square","triangle","triangleDown","star","diamond", "square", "square", "square", "square", "square"))

V(g1_equity)$shape<-"Null"

V(g1_equity)[which(V(g1_equity)$address=="Dallas, TX")]$color<-"blue"
V(g1_equity)[which(V(g1_equity)$address=="Houston, TX")]$color<-"red"
V(g1_equity)[which(V(g1_equity)$address=="Austin, TX")]$color<-"green"
V(g1_equity)[which(V(g1_equity)$address=="San Antonio, TX")]$color<-"yellow"

V(g1_equity)[which(V(g1_equity)$type=="NGO")]$shape<-"dot"
V(g1_equity)[which(V(g1_equity)$type=="Municipal/County")]$shape<-"square"
V(g1_equity)[which(V(g1_equity)$type=="State Agency")]$shape<-"triangle"
V(g1_equity)[which(V(g1_equity)$type=="Federal Agency")]$shape<-"triangleDown"
V(g1_equity)[which(V(g1_equity)$type=="University")]$shape<-"star"
V(g1_equity)[which(V(g1_equity)$type=="Private")]$shape<-"diamond"

V(g1_equity)$size<-V(g1_equity)$size*2

gvis_equity<-toVisNetworkData(g1_equity)
nodelist_equity<-gvis_equity$nodes


visNetwork(sort(gvis_equity$nodes),gvis_equity$edges, main="PT 2050 equity-focused Network",width = "100%",height = "850px") %>%
  visLayout(randomSeed = 123) %>%
  visEdges(smooth =T,
           arrows =list(to = list(enabled = TRUE, scaleFactor = .5)),
           color = list(color = "lightblue", highlight = "black"))  %>% 
  visPhysics(stabilization = FALSE)  %>%
  visIgraphLayout(smooth=FALSE,physics=FALSE, layout="layout_nicely") %>%
  visLayout(randomSeed = 123,improvedLayout = TRUE)%>%
  visInteraction(navigationButtons = TRUE)%>%
  visOptions(selectedBy = list(variable = c("county"), multiple = TRUE),
             highlightNearest = list(enabled = T, hover = T),
             nodesIdSelection = TRUE)%>%
  addFontAwesome() %>%
  visLegend(position = "left", addNodes = lnodes, useGroups = FALSE,stepY=100)

#plot(g1_equity)
```

#Resilience network
```{r echo=FALSE}
el_resilience<-el1[which(el1$Type2_resilience=="1"),]
e_resilience<-as.matrix(el_resilience)
g1_resilience<-graph_from_data_frame(d=e_resilience,directed=TRUE) 

#Define Attributes
for (i in 1:vcount(g1_resilience))
{
V(g1_resilience)[i]$county<-input_attributes$County[which(input_attributes$name==V(g1_resilience)[i]$name)]
V(g1_resilience)[i]$type<-input_attributes$Orgtype[which(input_attributes$name==V(g1_resilience)[i]$name)]
V(g1_resilience)[i]$address<-input_attributes$address[which(input_attributes$name==V(g1_resilience)[i]$name)]
V(g1_resilience)[i]$size<-input_attributes$TotalDegree[which(input_attributes$name==V(g1_resilience)[i]$name)]
}

lnodes <- data.frame(label = c("Non-Governmental","Municipal/County", "State Agency","Federal Agency","University","Private","Austin","Dallas", "Houston", "San Antonio", "Others"),
color.background = c("white", "white", "white", "white", "white","white","green", "blue","red", "yellow", "#87CEEB"),
color.border = c("black","black","black","black","black","black","black","black","black","black","black"),
shape=c("dot","square","triangle","triangleDown","star","diamond", "square", "square", "square", "square", "square"))

V(g1_resilience)$shape<-"Null"

V(g1_resilience)[which(V(g1_resilience)$address=="Dallas, TX")]$color<-"blue"
V(g1_resilience)[which(V(g1_resilience)$address=="Houston, TX")]$color<-"red"
V(g1_resilience)[which(V(g1_resilience)$address=="Austin, TX")]$color<-"green"
V(g1_resilience)[which(V(g1_resilience)$address=="San Antonio, TX")]$color<-"yellow"

V(g1_resilience)[which(V(g1_resilience)$type=="NGO")]$shape<-"dot"
V(g1_resilience)[which(V(g1_resilience)$type=="Municipal/County")]$shape<-"square"
V(g1_resilience)[which(V(g1_resilience)$type=="State Agency")]$shape<-"triangle"
V(g1_resilience)[which(V(g1_resilience)$type=="Federal Agency")]$shape<-"triangleDown"
V(g1_resilience)[which(V(g1_resilience)$type=="University")]$shape<-"star"
V(g1_resilience)[which(V(g1_resilience)$type=="Private")]$shape<-"diamond"

V(g1_resilience)$size<-V(g1_resilience)$size*2

gvis_resilience<-toVisNetworkData(g1_resilience)
nodelist_resilience<-gvis_resilience$nodes


visNetwork(sort(gvis_resilience$nodes),gvis_resilience$edges, main="PT 2050 Resilience-focused Network",width = "100%",height = "850px") %>%
  visLayout(randomSeed = 123) %>%
  visEdges(smooth =T,
           arrows =list(to = list(enabled = TRUE, scaleFactor = .5)),
           color = list(color = "lightblue", highlight = "black"))  %>% 
  visPhysics(stabilization = FALSE)  %>%
  visIgraphLayout(smooth=FALSE,physics=FALSE, layout="layout_nicely") %>%
  visLayout(randomSeed = 123,improvedLayout = TRUE)%>%
  visInteraction(navigationButtons = TRUE)%>%
  visOptions(selectedBy = list(variable = c("county"), multiple = TRUE),
             highlightNearest = list(enabled = T, hover = T),
             nodesIdSelection = TRUE)%>%
  addFontAwesome() %>%
  visLegend(position = "left", addNodes = lnodes, useGroups = FALSE,stepY=100)


```

```{r define attributes, include=FALSE}

#Define Attributes
for (i in 1:vcount(g1))
{
V(g1)[i]$county<-input_attributes$County[which(input_attributes$name==V(g1)[i]$name)]
V(g1)[i]$type<-input_attributes$Orgtype[which(input_attributes$name==V(g1)[i]$name)]
V(g1)[i]$address<-input_attributes$address[which(input_attributes$name==V(g1)[i]$name)]
}
```


#visualize Planet Texas network
```{r echo=FALSE}
#Define Attributes
for (i in 1:vcount(g1))
{
V(g1)[i]$county<-input_attributes$County[which(input_attributes$name==V(g1)[i]$name)]
V(g1)[i]$type<-input_attributes$Orgtype[which(input_attributes$name==V(g1)[i]$name)]
V(g1)[i]$address<-input_attributes$address[which(input_attributes$name==V(g1)[i]$name)]
V(g1)[i]$size<-input_attributes$inDegree1[which(input_attributes$name==V(g1)[i]$name)]
}

lnodes <- data.frame(label = c("Non-Governmental","Municipal/County", "State Agency","Federal Agency","University","Private","Austin","Dallas", "Houston", "San Antonio", "Others"),
color.background = c("white", "white", "white", "white", "white","white","green", "blue","red", "yellow", "#87CEEB"),
color.border = c("black","black","black","black","black","black","black","black","black","black","black"),
shape=c("dot","square","triangle","triangleDown","star","diamond", "square", "square", "square", "square", "square"))


V(g1)$shape<-"Null"

V(g1)[which(V(g1)$address=="Dallas, TX")]$color<-"blue"
V(g1)[which(V(g1)$address=="Houston, TX")]$color<-"red"
V(g1)[which(V(g1)$address=="Austin, TX")]$color<-"green"
V(g1)[which(V(g1)$address=="San Antonio, TX")]$color<-"yellow"

V(g1)[which(V(g1)$type=="NGO")]$shape<-"dot"
V(g1)[which(V(g1)$type=="Municipal/County")]$shape<-"square"
V(g1)[which(V(g1)$type=="State Agency")]$shape<-"triangle"
V(g1)[which(V(g1)$type=="Federal Agency")]$shape<-"triangleDown"
V(g1)[which(V(g1)$type=="University")]$shape<-"star"
V(g1)[which(V(g1)$type=="Private")]$shape<-"diamond"

V(g1)$size<-V(g1)$size*3

gvis1<-toVisNetworkData(g1)
nodelist1<-gvis1$nodes


pt2050network<-visNetwork(sort(gvis1$nodes),gvis1$edges, main="PT 2050 Network",width = "100%",height = "850px") %>%
  visLayout(randomSeed = 123) %>%
  visEdges(smooth =T,
           arrows =list(to = list(enabled = TRUE, scaleFactor = .5)),
           color = list(color = "lightblue", highlight = "black"))  %>% 
  visPhysics(stabilization = FALSE)  %>%
  visIgraphLayout(smooth=FALSE,physics=FALSE, layout="layout_nicely") %>%
  visLayout(randomSeed = 123,improvedLayout = TRUE)%>%
  visInteraction(navigationButtons = TRUE)%>%
  visOptions(selectedBy = list(variable = c("county"), multiple = TRUE),
             highlightNearest = list(enabled = T, hover = T),
             nodesIdSelection = TRUE)%>%
  addFontAwesome() %>%
  visLegend(position = "left", addNodes = lnodes, useGroups = FALSE,stepY=100)

pt2050network


```
#ego-centric network measures for subnetworks
```{r echo=FALSE}
#Degree in 

inDegreeR<-igraph::degree(g1_resilience,mode="in")
outDegreeR<-igraph::degree(g1_resilience,mode="out")
TotalDegreeR<-as.data.frame(igraph::degree(g1_resilience))
betweennessR<-igraph::betweenness(g1_resilience, v = V(g1_resilience), directed = TRUE, weights = NULL,
  nobigint = TRUE, normalized = TRUE)
inClosenessR<-igraph::closeness(g1_resilience, vids = V(g1_resilience), mode = c("in"),normalized = TRUE)
outClosenessR<-igraph::closeness(g1_resilience, vids = V(g1_resilience), mode = c("out"),normalized = TRUE)
DF_CentralityR<-as.data.frame(cbind(rownames(TotalDegreeR),inDegreeR,outDegreeR,TotalDegreeR,betweennessR,inClosenessR,outClosenessR))
rownames(DF_CentralityR)<-NULL
DF_CentralityR<-as.data.frame(DF_CentralityR)
colnames(DF_CentralityR)[1]<-"name"
colnames(DF_CentralityR)[4]<-"TotalDegreeR"

inDegreeE<-igraph::degree(g1_equity,mode="in")
outDegreeE<-igraph::degree(g1_equity,mode="out")
TotalDegreeE<-as.data.frame(igraph::degree(g1_equity))
betweennessE<-igraph::betweenness(g1_equity, v = V(g1_equity), directed = TRUE, weights = NULL,
  nobigint = TRUE, normalized = TRUE)
inClosenessE<-igraph::closeness(g1_equity, vids = V(g1_equity), mode = c("in"),normalized = TRUE)
outClosenessE<-igraph::closeness(g1_equity, vids = V(g1_equity), mode = c("out"),normalized = TRUE)
DF_CentralityE<-as.data.frame(cbind(rownames(TotalDegreeE),inDegreeE,outDegreeE,TotalDegreeE,betweennessE,inClosenessE,outClosenessE))
rownames(DF_CentralityE)<-NULL
DF_CentralityE<-as.data.frame(DF_CentralityE)
colnames(DF_CentralityE)[1]<-"name"
colnames(DF_CentralityE)[4]<-"TotalDegreeE"

inDegreeM<-igraph::degree(g1_meetings,mode="in")
outDegreeM<-igraph::degree(g1_meetings,mode="out")
TotalDegreeM<-as.data.frame(igraph::degree(g1_meetings))
betweennessM<-igraph::betweenness(g1_meetings, v = V(g1_meetings), directed = TRUE, weights = NULL,
  nobigint = TRUE, normalized = TRUE)
inClosenessM<-igraph::closeness(g1_meetings, vids = V(g1_meetings), mode = c("in"),normalized = TRUE)
outClosenessM<-igraph::closeness(g1_meetings, vids = V(g1_meetings), mode = c("out"),normalized = TRUE)
DF_CentralityM<-as.data.frame(cbind(rownames(TotalDegreeM),inDegreeM,outDegreeM,TotalDegreeM,betweennessM,inClosenessM,outClosenessM))
rownames(DF_CentralityM)<-NULL
DF_CentralityM<-as.data.frame(DF_CentralityM)
colnames(DF_CentralityM)[1]<-"name"
colnames(DF_CentralityM)[4]<-"TotalDegreeM"

DF_CentralityM<-merge(DF_CentralityM, DF_CentralityE, by = "name")
DF_CentralityR<-merge(DF_CentralityR, DF_CentralityM, by = "name")
txengocentrality<-merge(txengocentrality, DF_CentralityR, by = "name")
write.csv(txengocentrality,file = "TX ENGO Centrality.csv")



attr_nodelist<-merge(attr_nodelist, txengocentrality, by = "name",all.x = TRUE)
write.csv(attr_nodelist,file = "Nodelist.csv")


```


```{r save}

setwd("C:/Users/tenis/Desktop/Data_Projects/pt2050/")
write_rds(g1, "data/network_full.rds")
write_rds(g1_equity, "data/network_equity.rds")
write_rds(g1_resilience, "data/network_resilience.rds")


```

#visualize Planet Texas Funder network
##Not READY
{r echo=FALSE}
#Define Attributes
for (i in 1:vcount(g2))
{
V(g2)[i]$county<-input_attributes$County[which(input_attributes$name==V(g2)[i]$name)]
V(g2)[i]$type<-input_attributes$Orgtype[which(input_attributes$name==V(g2)[i]$name)]
V(g2)[i]$address<-input_attributes$address[which(input_attributes$name==V(g2)[i]$name)]
V(g2)[i]$size<-input_attributes$inDegree1[which(input_attributes$name==V(g2)[i]$name)]
}

lnodes <- data.frame(label = c("Non-Governmental","Municipal/County", "State Agency","Federal Agency","University","Private","Austin","Dallas", "Houston", "San Antonio", "Others"),
color.background = c("white", "white", "white", "white", "white","white","green", "blue","red", "yellow", "#87CEEB"),
color.border = c("black","black","black","black","black","black","black","black","black","black","black"),
shape=c("dot","square","triangle","triangleDown","star","diamond", "square", "square", "square", "square", "square"))


V(g2)$shape<-"Null"

V(g2)[which(V(g2)$address=="Dallas, TX")]$color<-"blue"
V(g2)[which(V(g2)$address=="Houston, TX")]$color<-"red"
V(g2)[which(V(g2)$address=="Austin, TX")]$color<-"green"
V(g2)[which(V(g2)$address=="San Antonio, TX")]$color<-"yellow"

V(g2)[which(V(g2)$type=="NGO")]$shape<-"dot"
V(g2)[which(V(g2)$type=="Municipal/County")]$shape<-"square"
V(g2)[which(V(g2)$type=="State Agency")]$shape<-"triangle"
V(g2)[which(V(g2)$type=="Federal Agency")]$shape<-"triangleDown"
V(g2)[which(V(g2)$type=="University")]$shape<-"star"
V(g2)[which(V(g2)$type=="Private")]$shape<-"diamond"

V(g2)$size<-V(g2)$size*3

gvis2<-toVisNetworkData(g2)
nodelist2<-gvis2$nodes


visNetwork(sort(gvis2$nodes),gvis2$edges, main="PT 2050 Funder Network",width = "100%",height = "850px") %>%
  visLayout(randomSeed = 123) %>%
  visEdges(smooth =T,
           arrows =list(to = list(enabled = TRUE, scaleFactor = .5)),
           color = list(color = "lightblue", highlight = "black"))  %>% 
  visPhysics(stabilization = FALSE)  %>%
  visIgraphLayout(smooth=FALSE,physics=FALSE, layout="layout_nicely") %>%
  visLayout(randomSeed = 123,improvedLayout = TRUE)%>%
  visInteraction(navigationButtons = TRUE)%>%
  visOptions(selectedBy = list(variable = c("county"), multiple = TRUE),
             highlightNearest = list(enabled = T, hover = T),
             nodesIdSelection = TRUE)%>%
  addFontAwesome() %>%
  visLegend(position = "left", addNodes = lnodes, useGroups = FALSE,stepY=100)
